Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-28 vesicle_code/docs/permeableVes/main.tex

Using scaling arguments, we showed that permeability due to osmolarity
is two orders of magnitude larger than permeability due to tension, and
six orders of magnitude larger than permeability due to bending.
Therefore, future studies will investigate semi-permeability in the
presence of a solute concentration. The presence of such a solute
concentrations is responsible for many physiological processes including
cell migration in confined
microenvironments~\cite{StrokaJiangChenEtAl2014_Cell},
dialysis~\cite{wan2006}, and
apoptosis~\cite{marchetti1996mitochondrial}. We plan to investigate
vesicle motion in a solute in the zero Peclet number limit which was
analyzed for spherical vesicles by Anderson~\cite{and1983} and more
general shapes using a finite element method by Jaeger {\em et
al.}~\cite{jae-car-med-try1999}.

>>>>

Using scaling arguments, we showed that permeability due to osmolarity
is two orders of magnitude larger than permeability due to tension, and
six orders of magnitude larger than permeability due to bending.
Therefore, future studies will investigate semi-permeability in the
presence of a solute concentration. The presence of such a solute
concentrations is responsible for many physiological processes including
cell migration in confined
microenvironments~\cite{StrokaJiangChenEtAl2014_Cell},
dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect} and
apoptosis~\cite{marchetti1996mitochondrial}. We plan to investigate
vesicle motion in a solute in the zero Peclet number limit which was
analyzed for spherical vesicles by Anderson~\cite{and1983} and more
general shapes using a finite element method by Jaeger {\em et
al.}~\cite{jae-car-med-try1999}.
